Paper Analysis

### 2025-04-11 Paper_WriteUp/Paper_Plots.qmd
updating height/width and removing 5game in fig2b

ggsave(plot = fig2a, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "time_between_games_gm.png")), dpi = 600,
       height = 5, width = 7)

session_length_plot_gm <- ggplot(gm_session_lengths_df, aes(x = session_length)) +
  geom_histogram() +
  scale_x_continuous(
    trans = pseudo_log_trans(sigma = 2.36),
    breaks = c(1, 5, 10, 100),
    labels = c("1 game", "5 games", "10 games", "100 games"),
    limits = c(0, 389)
  ) +
  xlab("Number of Games in a Session (Log Scale)") +
  ylab("Frequency") #+ ggtitle("Number of Games per Session for GMs")
fig2b <- session_length_plot_gm + theme_single_y()

ggsave(plot = fig2b, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "session_length_gm.png")), dpi = 600,
       height = 5, width = 7)
```

>>>>

ggsave(plot = fig2a, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "time_between_games_gm.png")), dpi = 600,
       height = 4, width = 6.25)

session_length_plot_gm <- ggplot(gm_session_lengths_df, aes(x = session_length)) +
  geom_histogram() +
  scale_x_continuous(
    trans = pseudo_log_trans(sigma = 2.36),
    breaks = c(1, 10, 100),
    labels = c("1 game", "10 games", "100 games"),
    limits = c(0, 389)
  ) +
  xlab("Number of Games in a Session (Log Scale)") +
  ylab("Frequency") #+ ggtitle("Number of Games per Session for GMs")
fig2b <- session_length_plot_gm + theme_single_y()

ggsave(plot = fig2b, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "session_length_gm.png")), dpi = 600,
       height = 4, width = 6.25)
```
